Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
actually made graphs show up for real this time

```{r eval=FALSE}
cleaned_data <- labelled::to_factor(cleaned_data)

@@

# Plot age_group
perc_age_group <- cleaned_data %>% count(age_group) %>% mutate(perc = n/nrow(cleaned_data))
age_group <- perc_age_group %>% ggplot(aes(x = age_group, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Age of Respondents in 2018 ACS data",
                                                                               x = "Age Group", y = "Percentage", subtitle = "Figure X")
```

```{r post-strat graphs}
race

gender

education

state

age_group
```

@@

# References
R
Survey and ACS dataset
https://www.voterstudygroup.org/uploads/reports/Data/Nationscape-User-Guide_2020sep10.pdf
https://www.voterstudygroup.org/uploads/reports/Data/NS-Methodology-Representativeness-Assessment.pdf
Wu
https://www.pewresearch.org/fact-tank/2020/10/26/what-the-2020-electorate-looks-like-by-party-race-and-ethnicity-age-education-and-religion/
Tausanovitch, Chris and Lynn Vavreck. 2020. Democracy Fund + UCLA Nationscape, October 10-17, 2019 (version 20200814). Retrieved from [URL].

>>>>

```{r create post-strat graphs, message=FALSE, echo=FALSE}
cleaned_data <- labelled::to_factor(cleaned_data)

@@

# Plot age_group
perc_age_group <- cleaned_data %>% count(age_group) %>% mutate(perc = n/nrow(cleaned_data))
age_group <- perc_age_group %>% ggplot(aes(x = age_group, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Age of Respondents in 2018 ACS data",
                                                                               x = "Age Group", y = "Percentage", subtitle = "Figure X")
```
```{r post-strat graphs,fig.height=6, message=FALSE, echo=FALSE}
race
education
gender
state
age_group
```

@@

# References
R
Survey and ACS dataset
https://www.voterstudygroup.org/uploads/reports/Data/Nationscape-User-Guide_2020sep10.pdf
https://www.voterstudygroup.org/uploads/reports/Data/NS-Methodology-Representativeness-Assessment.pdf
Wu
https://www.pewresearch.org/fact-tank/2020/10/26/what-the-2020-electorate-looks-like-by-party-race-and-ethnicity-age-education-and-religion/
ACS stuff:
https://www2.census.gov/geo/pdfs/education/Uhl_CAS_2011.pdf
https://www.census.gov/programs-surveys/acs/technical-documentation/errata/120.html
https://usa.ipums.org/usa/resources/voliii/formACS2018.pdf
https://usa.ipums.org/usa/resources/codebooks/ACS_codebook.pdf
https://www.politifact.com/factchecks/2014/jan/09/us-census-bureau/americans-must-answer-us-census-bureau-survey-law-/

Tausanovitch, Chris and Lynn Vavreck. 2020. Democracy Fund + UCLA Nationscape, October 10-17, 2019 (version 20200814). Retrieved from [URL].
